---
title: "Apprentissage Statistique"
subtitle: "New York city Airbnb"
author: "Duong Nguyen & Julien Le Mauff"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  pdf_document: default
---

```{r setup, include=F, warning=FALSE, message=FALSE}
knitr::opts_chunk$set(echo = T)
```

# Import Packages

```{r cache=TRUE,include=F,message=FALSE, warning=FALSE}
library(caret)
library(dplyr)
library(psych)
library(caret)
library(ggplot2)
library(ggmap)
library(lubridate)
library(stringr)
library(forcats)
library(gridExtra)
```

# Import data

## Listing

```{r cache=TRUE,include=F,message=FALSE, warning=FALSE}
# listing <- read.csv("/Users/ngyduong/Documents/Machine Learning/Github_projects/NewYork_Airbnb/NYC_Airbnb/Data/listings.csv", sep = ",")
# 
# listings_keep <- c("id", "price","last_review","host_id",
#                    "host_is_superhost", "host_identity_verified",
#                    "neighbourhood_group_cleansed", "neighbourhood_cleansed",
#                    "latitude","longitude", "property_type", "accommodates",
#                    "bedrooms", "beds", "bed_type", "cleaning_fee",
#                    "minimum_nights", "availability_365", "number_of_reviews",
#                    "review_scores_rating","cancellation_policy")
# 
# listing <- listing[listing$state=="NY", listings_keep]
# names(listing)[names(listing) == 'id'] <- 'listing_id'
```

## Calendar

```{r cache=TRUE,include=F,message=FALSE, warning=FALSE}
# calendar <- read.csv("/Users/ngyduong/Documents/Machine Learning/Github_projects/NewYork_Airbnb/NYC_Airbnb/Data/calendar.csv", sep = ",")
# 
# calendar$adjusted_price = as.numeric(gsub("[\\$,]", "", calendar$adjusted_price))
# 
# calendar_grouped <- group_by(calendar, listing_id) %>%
#   summarise(adjusted_price = mean(adjusted_price))
```

## Merge Calendar and Listing

```{r cache=TRUE,include=F,message=FALSE, warning=FALSE}
# data <- merge(calendar_grouped, listing, by = "listing_id")
```

## Removing $ sign on price and cleaning fees

```{r cache=TRUE,include=F,message=FALSE, warning=FALSE}
# data$price = as.numeric(gsub("[\\$,]", "", data$price))
# data$cleaning_fee = as.numeric(gsub("[\\$,]", "", data$cleaning_fee))
```

## Export the compiled data base

```{r cache=TRUE,include=F,message=FALSE, warning=FALSE}
# write.csv(data, "/Users/ngyduong/Documents/Machine Learning/Github_projects/NewYork_Airbnb/NYC_Airbnb/Data/compiled_data.csv",
#           row.names = FALSE)
```

# Import compiled data

```{r cache=TRUE,include=F,message=FALSE, warning=FALSE}
# data <- read.csv("/Users/ngyduong/Documents/Machine Learning/Github_projects/NewYork_Airbnb/NYC_Airbnb/Data/compiled_data.csv", sep = ",")
```

## Data manipulations / Cleaning the data

### Dealing with missing values

```{r cache=TRUE,include=F,message=FALSE, warning=FALSE}
# na_count <- t(data %>% summarise_each(funs(sum(is.na(.)))))
# 
# # ===== ===== Price ===== ===== 
# 
# # We replace the 8 missing values of adjusted price by the price
# # (not adjusted) since there is only a slight difference
# # between the 2 variables
# 
# data[is.na(data$adjusted_price),
#      "adjusted_price"] <- data[is.na(data$adjusted_price),"price"]
# 
# # We then drop the variable "price"
# data <- data[ , !(names(data) %in% c("price"))]
# 
# # We change the name adjusted_price by price for more convenience
# names(data)[names(data) == "adjusted_price"] <- "price"
# 
# # ===== ===== Bedrooms ===== =====
# 
# histogram(data$bedrooms)
# mean(data$bedrooms, na.rm = T)
# median(data$bedrooms, na.rm = T)
# 
# # Given the distribution, we can replace the 76 missing values
# # of bedrooms (the number of bedrooms) by the median grouped 
# # by property type, number of accomodates and bed types. 
# 
# # We use the median because we want an integer and not a float 
# # (numbers with commas)
# 
# data <- data %>%
#   group_by(
#     property_type,
#     accommodates,
#     bed_type) %>%
#   mutate(bedrooms=ifelse(is.na(bedrooms),
#                          median(bedrooms,na.rm = T),bedrooms)) %>%
#   ungroup()
# 
# # ===== ===== Beds ===== ===== 
# 
# histogram(data$beds)
# mean(data$beds, na.rm = T)
# median(data$beds, na.rm = T)
# 
# # Given the distribution, we can replace the 479 missing values 
# # of beds (the number of beds) by the median grouped 
# # by property type, number of accomodates and bed types. 
# 
# # We use the median because we want an integer and not a float 
# # (numbers with commas)
# 
# data <- data %>%
#   group_by(
#     property_type,
#     accommodates,
#     bed_type) %>% 
#   mutate(beds=ifelse(is.na(beds),
#                          median(beds,na.rm=T),beds)) %>%
#   ungroup()
# 
# # There is still 2 missing values for beds, we will replace the 
# # last 2 missing values by the overall median of beds
# 
# data[is.na(data$beds), "beds"] <- median(data$beds, na.rm = T)
# 
# # ===== ===== Cleaning fee ===== ===== 
# 
# # A cleaning fee is a one-time fee charged by hosts to cover the cost of
# # cleaning their holiday rental when guests depart. Not all hosts charge
# # this fee. Some incorporate it into their nightly rate. 
# 
# # Therefore it is safe to assume that when there is no value for this
# # variable it simply means that the host didn't charge
# 
# data[is.na(data$cleaning_fee), "cleaning_fee"] <- 0
# 
# # ===== ===== Review scores rating ===== ===== 
# 
# histogram(data$review_scores_rating)
# 
# # Given that the distribution is skewed on the right, we will use the
# # median to approximate the missing values grouped by neighbours, 
# # property types, type of beds and if the host is a superhost.
# 
# data <- data %>%
#   group_by(
#     neighbourhood_cleansed,
#     bed_type,
#     property_type,
#     host_is_superhost) %>% 
#   mutate(review_scores_rating=ifelse(is.na(review_scores_rating),
#                          median(review_scores_rating,na.rm=T),
#                          review_scores_rating)) %>%
#   ungroup()
#
# # There is still 202 missing values so we will just replace them with the
# # overall score median
#
# data[is.na(data$review_scores_rating),
#      "review_scores_rating"] <- median(data$review_scores_rating,
#                                        na.rm = T)
#
# ===== ===== Host is superhost ===== =====
# 
# # There is only 5 missing values (blank) out of more than 50 000
# # Therefore we will just replace them with the most common value (f)
# 
# most_common_superhost <- 
#   tail(names(sort(table(data$host_is_superhost))), 1)
# 
# data <- data %>%
#   mutate_if(is.factor, 
#             funs(factor(replace(., .=="", most_common_superhost))))
# 
# # ===== ===== Host identity verified ===== =====
# 
# # There is only 5 missing values (blank) out of more than 50 000
# # Therefore we will just replace them with the most common value (f)
# 
# most_common_verified <- 
#   tail(names(sort(table(data$host_identity_verified))), 1)
# 
# data <- data %>%
#   mutate_if(is.factor, 
#             funs(factor(replace(., .=="", most_common_verified))))
```

### Dealing with categorical variables with too many levels

```{r cache=TRUE,include=F,message=FALSE, warning=FALSE}
# # # ===== ===== Type de logement ===== =====
# 
# # We groups all 40 subgroups of logement types into 5 big groups
# 
# Appartment <- c("Aparthotel","Serviced apartment", "Loft",
#                 "Condominium", "Apartment")
# 
# House <- c("Barn", "Timeshare", "Dome house", "Lighthouse",
#            "Casa particular (Cuba)", "Houseboat", "Villa",
#            "Treehouse", "Earth house", "Cottage", "Tiny house",
#            "Townhouse", "House")
# 
# Shared_room <- c("Dorm", "Hostel", "Guesthouse")
# 
# Private_room <- c("Farm stay", "Bed and breakfast", "Resort", "Hotel",
#                    "Boutique hotel", "Guest suite", "In-law")
# 
# Other <- c("Train", "Bus", "island", "Boat", "Other", "Cave", "Island",
#            "Camper/RV", "Bungalow", "Cabin", "Yurt", "Castle", "Tent")
# 
# data$property_type <- as.character(data$property_type)
# 
# data <- 
#   mutate(data, 
#          property_type = ifelse(property_type %in% Appartment,
#                                 "Appartment", property_type),
#          property_type = ifelse(property_type %in% House,
#                                 "House", property_type),
#          property_type = ifelse(property_type %in% Shared_room,
#                                 "Shared Room", property_type),
#          property_type = ifelse(property_type %in% Private_room,
#                                 "Private Room", property_type),
#          property_type = ifelse(property_type %in% Other,
#                                 "Others", property_type))
# 
# data$property_type <- as.factor(data$property_type)
```

## Export the cleaned database 

```{r cache=TRUE,include=F,message=FALSE, warning=FALSE}
# write.csv(data, "/Users/ngyduong/Documents/Machine Learning/Github_projects/NewYork_Airbnb/NYC_Airbnb/Data/clean_data.csv",
#           row.names = FALSE)
```

# Data analysis / Data visualisation

## Import the clean database

```{r cache=TRUE,include=F,message=FALSE, warning=FALSE}
data <- read.csv("/Users/ngyduong/Documents/Machine Learning/Github_projects/NewYork_Airbnb/NYC_Airbnb/Data/clean_data.csv", 
                 sep = ",")

data$host_id <- as.factor(data$host_id)
data$bedrooms <- as.factor(data$bedrooms)
data$beds <- as.factor(data$beds)
data$accommodates <- as.factor(data$accommodates)
```

## Data visualisation

```{r cache=TRUE,include=F,message=FALSE, warning=FALSE}
theme <- theme(plot.title = element_text(hjust = 0.5), 
               plot.background = element_rect(fill = "#BFD5E3"))
tag_source <- "Source: Inside Airbnb"
```

### Density of discrete variables

```{r cache=TRUE,include=T,message=FALSE, warning=FALSE, echo=F}
features_discrete <- names(select_if(data[,-c(1,3:4)],is.factor))
# Without host_id, last_review and listing_id

for (i in features_discrete) {
  plot <-ggplot(mapping = aes_string(x = fct_infreq(data[,i]), 
                                     fill = data[,i])) +
    geom_bar(width = 1, colour = "black", show.legend = F) + 
    theme + labs(x = "", y = "Fréquence", caption = tag_source) +
    ggtitle(i)
  print(plot)
}
```

### Density and log of continuous variables 

```{r cache=TRUE,include=T,message=FALSE, warning=FALSE, echo=F}
features_numeric <- names(select_if(data[,-c(1,9:10)],is.numeric))
# Without listing_id, latitude and longitude

for (i in features_numeric){
  
  plot <- ggplot(mapping = aes(x = data[,i])) +
    geom_histogram(colour="black", fill="dodgerblue3",
                   aes(y = ..density..)) + theme + ggtitle(i) +
    labs(x = "", y = "Density", caption = tag_source) + 
    geom_density(fill = "cyan", colour = "cyan", 
                 alpha = 0.5, lwd=0.5, linetype = "dashed") 
  
  log_plot <- ggplot(mapping = aes(x = log(data[,i]))) +
    geom_histogram(colour="black", fill="forestgreen",
                   aes(y= ..density..)) + theme + 
    labs(x = "", y = "Density", caption = tag_source) + 
    ggtitle(paste("log of",i)) +
    geom_density(fill = "olivedrab2", colour = "olivedrab2", 
                 alpha = 0.5, lwd=0.5, linetype = "dashed") 
  
  grid.arrange(plot, log_plot, ncol=2)
}
```

### Boxplot 

```{r cache=TRUE,include=T,message=FALSE, warning=FALSE, echo=F}
# # ===== ===== Prix par arrondissement ===== =====

ggplot(data, mapping = aes(x = neighbourhood_group_cleansed, 
                           y = log(price))) +
  geom_boxplot(outlier.colour = "darkblue", outlier.size = 0.5,
               color="deepskyblue", fill="cyan", alpha=0.2) + 
  ggtitle("Prix des airbnb par nuit en moyenne par arondissement") +
  labs(x = "Arrondissements", y = "Prix par nuit en moyenne (en log)",
       caption = tag_source) + theme

# # ===== ===== Prix par arrondissement et type de logement ===== =====

ggplot(data, mapping = aes(x = neighbourhood_group_cleansed, 
                           y = log(price), 
                           fill = property_type)) +
  geom_boxplot(outlier.colour = "darkblue", outlier.size = 0.5) + 
  ggtitle("Prix des airbnb par nuit en moyenne par arondissement \n 
          et par type de logement") +
  scale_fill_discrete(name = "Type de logement") + theme +
  labs(x = "Arrondissement", y = "Prix par nuit en moyenne (en log)",
       caption = tag_source) 
```